### 2019-09-15 paper/HOLMultivariate.tex
Updated generated TeX theories

\newcommand{\HOLMultivariateDate}{13 Settembre 2019}
\newcommand{\HOLMultivariateTime}{10:02}

@@

       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}

@@

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}. \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}

@@

@@

   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrecYY}
       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
\newcommand{\HOLMultivariateTheoremscontextXXrecYY}{\UseVerbatim{HOLMultivariateTheoremscontextXXrecYY}}

@@

       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}

@@

       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}

@@

@@

           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}

@@

                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}

@@

           \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}

@@

                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}

@@

       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}. \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}

@@

               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrecYY}
       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrecYY}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrecYY}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}
       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}}

@@

        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)}

@@

@@

@@

\HOLThmTag{Multivariate}{context_rec'}\HOLMultivariateTheoremscontextXXrecYY

@@

\HOLThmTag{Multivariate}{weakly_guarded_rec'}\HOLMultivariateTheoremsweaklyXXguardedXXrecYY
\HOLThmTag{Multivariate}{weakly_guarded_rec_rule}\HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule

>>>>

\newcommand{\HOLMultivariateDate}{15 Settembre 2019}
\newcommand{\HOLMultivariateTime}{21:28}

@@

       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Es}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDRYY}
       \HOLConst{FEVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}. \HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDRYY}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDRYY}}

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXsing}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}. \ensuremath{[}\ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLBoundVar{X}\ensuremath{]}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXsing}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXsing}}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E} \HOLConst{DELETE} \HOLBoundVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E} \HOLConst{DELETE} \HOLBoundVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}

@@

                   \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}

@@

           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}

@@

                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                    \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}

@@

           \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}

@@

                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                   \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}. \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}

@@

               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
               \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E} \HOLConst{DELETE} \HOLBoundVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

@@

   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.

@@

\HOLThmTag{Multivariate}{CCS_SUBST_FOLDR'}\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDRYY

@@

\HOLThmTag{Multivariate}{CCS_SUBST_sing}\HOLMultivariateTheoremsCCSXXSUBSTXXsing

@@

@@
